Robust Subspace and Higher Moments Distances for Botnet Detection

### 2019-04-25 docs/papers/2019JNCA_m-rpca/2019JNCA_m-rpca.tex
moved to botnets references and stop at bothunter

Botnets...

@@

Network anomaly detection problems are usually characterized by skewed and imbalanced data \cite{Phua2004minority,he2008learning}. Learning algorithms for imbalanced data has been a challenging research topic. The fundamental issue with the imbalanced learning problem is the ability of imbalanced data to significantly compromise the performance of most standard learning algorithms \cite{he2008learning}. He and Garcia \cite{he2008learning} present a classification of imbalanced learning methods as sampling, cost-sensitive learning, kernel-based, and active learning. Some techniques can make the data discriminative for better discriminative analytics: Data engineering (i.e. sampling \cite{he2008learning}, aggregation \cite{callegari2011novel, acarali2016survey}); Feature extraction (i.e. decomposition \cite{vaswani2018robust}, robust estimates \cite{zhou2017anomaly}). To face a high imbalanced data set, we adopt a sampling method based on data aggregation for discriminative feature generation, considering that data aggregation is a widely adoted approach for feature engineering \cite{chandrashekar2014survey,acarali2016survey} and network anomaly detection \cite{lakhina2005mining, callegari2011novel, vieira2017model}.

@@

@@

\cite{gu2008botminer} (Botminer: Clustering analysis of network traffic for protocol-and structure-independent botnet detection)

@@

@@

@@

Based on related works \cite{lakhina2005mining, callegari2011novel, chandrashekar2014survey, acarali2016survey} and experience \cite{vieira2017model, galibus2017offline}, we selected some features for improving the anomaly detection.
The features are generated by a data aggregation into a selected window size. We evalute our proposal for windows with 0.15, 0.25, 1 and 2 seconds, for each scenario of the CTU-13 data set.

>>>>

Botnets have emerging as a key threat for cyber security, considering that Botnets are the key platform for many Internet attacks (i.e. spam, distributed denial-of-service (DDoS), identity theft, and phishing). Most of the current botnet detection approaches work only on specific botnet command and control (. Lots of efforts are directed to avoid attacks from known attackers, however attacks from one source is not real nowadays, since the attacks are usualy from distributed botnets that change their approaches frequently, in order to avoid behavioral or pattern based detecions. This changing behavior is known as adversarial model \cite{gu2008botminer, garcia2014empirical,khattak2015botflex,acarali2016survey,wang2017botnet,da2018online,Wang2018ddosbotnets}.

@@

Network anomaly detection problems are usually characterized by skewed and imbalanced data \cite{Phua2004minority,he2008learning}. Learning algorithms for imbalanced data has been a challenging research topic. The fundamental issue with the imbalanced learning problem is the ability of imbalanced data to significantly compromise the performance of most standard learning algorithms \cite{he2008learning}. He and Garcia \cite{he2008learning} present a classification of imbalanced learning methods as sampling, cost-sensitive learning, kernel-based, and active learning. Some techniques can make the data discriminative for better discriminative analytics: Data engineering (i.e. sampling \cite{he2008learning,gu2008botminer}, aggregation \cite{lakhina2005mining,gu2008botminer,callegari2011novel, acarali2016survey}); Feature extraction (i.e. decomposition \cite{vaswani2018robust}, robust estimates \cite{zhou2017anomaly}). To face a high imbalanced data set, we adopt a sampling method based on data aggregation for discriminative feature generation, considering that data aggregation is a widely adoted approach for feature engineering \cite{chandrashekar2014survey,acarali2016survey} and network anomaly detection \cite{lakhina2005mining, callegari2011novel, vieira2017model}.

@@

Botnets are becoming one of the most serious threats to Internet security. A botnet is a network of compromised machines under the influence of malware (bot) code. The botnet is commandeered by a “botmaster” and utilized as “resource” or “platform” for attacks such as distributed denial-of-service (DDoS) attacks, and fraudulent activities such as spam, phishing, identity theft, and information exfiltration. In order for a botmaster to command a botnet, there needs to be a command and control (C&C) channel through which bots receive commands and coordinate attacks and fraudulent activities. The C&C channel is the means by which individual bots form a botnet. Centralized C&C structures using the Internet Relay Chat (IRC) protocol have been utilized by botmasters for a long time. In this architecture, each bot logs into an IRC channel, and seeks commands from the botmaster. Even today, many botnets are still designed this way. Quite a few botnets, though, have begun to use other protocols such as HTTP [8, 14, 24, 39], probably because HTTP-based C&C communications are more stealthy given that Web traffic is generally allowed in most networks \cite{gu2008botminer}.

@@

\cite{gu2008botminer} (Botminer: Clustering analysis of network traffic for protocol-and structure-independent botnet detection). The objective of BotMiner is to detect groups of compromised machines within a monitored network that are part of a botnet. This framework monitors both who is talking to whom that may suggest C&C communication activities and who is doing what that may suggest malicious activities, and finds a coordinated group pattern in both kinds of activities. The detection framework clusters similar communication activities in the C-plane (C&C communication traffic), clusters similar malicious activities in the A-plane (activity traffic), and performs cross cluster correlation to identify the hosts that share both similar communication patterns and similar malicious activity patterns.

@@

\cite{gu2007bothunter} (Bothunter: Detecting malware infection through ids-driven dialog correlation). The BotHunter method was proposed by Gu et al. (2007) to detect the infection and coordination dialog of botnets by matching a state-based infection sequence model. It consists of a correlation engine that aims at detecting specific stages of the malware infection process, such as inbound scanning, exploit usage, egg downloading, outbound bot coordination dialog and outbound attack propagation.

@@

\cite{Wang2018ddosbotnets} present an in-depth analysis based on 50,704 different Internet DDoS attacks launched by 674 botnets from 23 different botnet families. Geospatial distribution of the attacking sources follows certain patterns, multiple attacks to the same target also exhibit strong patterns of inter-attack time interval, there is a trend for different botnets to launch DDoS attacks targeting the same victim, simultaneously or in turn.

@@

Based on related works \cite{lakhina2005mining,gu2008botminer,callegari2011novel,chandrashekar2014survey,acarali2016survey} and experience \cite{vieira2017model, galibus2017offline}, we selected some features for improving the anomaly detection.
The features are generated by a data aggregation into a selected window size. We evalute our proposal for windows with 0.15, 0.25, 1 and 2 seconds, for each scenario of the CTU-13 data set.
